\documentclass{article}

\usepackage{mystyle}

\begin{document}
\title{Problem Solving Club Constitution}
\author{Andrew Helwer}
\date{February 2013}
\maketitle

\section{Article 1: Name}

The name of the organization shall be Problem Solving Club, hereinafter referred to as the PSC.

\section{Article 2: Mission}

The PSC will train students for competition in top-flight programming contests, organize programming contest events at the University of Calgary, and provide students with an outlet and opportunity to pursue knowledge of computer science and mathematics beyond that which is available in class.
The PSC will train students with faculty and alumni guidance, aiming to conduct coached practices at least once per week. 
The PSC will receive funding for events and expenses from the Department of Computer Science and also private corporations, offering them opportunities such as recruitment and sponsorship.
The PSC will further provide a platform for students to research and present algorithmic and mathematical concepts to a group of their peers, and have such concepts presented to them in turn.

\section{Article 3: Membership}

PSC membership is open to both graduate and undergraduate students at the University of Calgary.
University of Calgary faculty and alumni are permitted membership provided they they operate in a capacity which provides coaching or mentorship to student members of the PSC.
The PSC will have a minimum of twenty members at all times, two-thirds of which are active members of the Students' Union.
The PSC will charge a membership fee of \$5.00.
This membership will be recognized for the term September to August.

\section{Article 4: Students' Union}

PSC acknowledges and will abide by the Students' Union By-laws and Policies unless otherwise approved by the Club Committee.
We are aware that PSC will no longer remain a Students' Union club if a Policy or By-law is contravened without Club Committee ratification.

\section{Article 5: Office and Duties}

The Executive and their respective duties of PSC shall consist of:
\begin{itemize}
    \item President
        \begin{itemize}
            \item Required to attend all club meetings, or have a VP attend in stead.
            \item Shall adhere to the PSC constitution.
            \item Shall be responsible for coordinating the organization of club events.
            \item Shall ensure all members are given adequate opportunity to excel.
            \item Shall have co-signing authority for all club financial transations.
            \item Shall be responsible for submitting the annual club report.
        \end{itemize}
    \item VP Operations
        \begin{itemize}
            \item Required to attend the majority of club meetings.
            \item Shall adhere to the PSC constitution.
            \item Shall coordinate topics and dates of student research lectures.
            \item Shall set up and maintain club IT infrastructure.
        \end{itemize}
    \item VP Finance
        \begin{itemize}
            \item Required to attend the majority of club meetings.
            \item Shall adhere to the PSC constitution.
            \item Shall have co-signing authority for all club financial transations.
            \item Will prepare budgets and expenditure reports for all club events.
        \end{itemize}
    \item VP External
        \begin{itemize}
            \item Required to attend the majority of club meetings.
            \item Shall adhere to the PSC constitution.
            \item Shall maintain relations with sponsors and other organizations.
            \item Shall seek to establish new relationships with third parties.
        \end{itemize}
\end{itemize}

\section{Article 6: Executive Terms of Office}

The term of office for all Executive positions shall commence May 1st and end on April 30th of the following school year. 

\section{Article 7: Executive Elections}

\begin{enumerate}
    \item The election of a new club Executive must take place no later than March 31st of each year to ensure a smooth transition from old Executive to new Executive. 
    \item Prior to the election, the Executive shall appoint a Chief Election Officer (CEO) for the upcoming election. The CEO must be a person who is not running in the upcoming election. 
    \item The CEO shall not vote in the upcoming election. 
    \item The CEO shall be responsible for all duties associated with the upcoming election and shall provide proper notice to all club members of the upcoming election.
\end{enumerate}

\section{Article 8: Transition of the Executive}

\begin{enumerate}
    \item During the period from the end of the club elections to the end of the Executive term, the outgoing Executive must orient the newly-elected Executive in the conduct of their duties.
        This includes (but is not limited to) enabling access to and relinquishing control of:
        \begin{itemize}
            \item PSC email address
            \item PSC mailing list
            \item PSC website
            \item PSC business and faculty contacts
            \item PSC accounts with assorted websites and services
        \end{itemize}
        It is the responsibility of the outgoing Executive to mentor the newly-elected Executive so as to ensure a smooth transition, and to equip them with skills and knowledge such that the effectiveness of the club is not degraded.
    \item It is the responsibility of the departing President to ensure that all club requirements to the Students' Union, including submission of a complete annual report and the removal of all club records and materials from the club office and locker, have been fulfilled before the incoming Executive assumes office.
    \item It is the responsibility of the departing President and VP Finance to bring all accounts up to date to the end of the fiscal year, and to prepare any required financial statements of the club. 
In addition, the outgoing President and VP Finance must arrange with the respective incoming Executive for the transition of the club bank accounts into the incoming President's and VP Finance's names. These tasks are to be completed and their outputs delivered to the new Executive no later than the last day of April.
    \item It is the responsibility of the incoming Executive to assume custody of all club records and materials and accountability for all financial activities of the club (as outlined in Article 5) and for all club requirements to the Students' Union commencing with the first day of May.
\end{enumerate}

\section{Article 9: Meetings}

There shall be at least one Executive meeting per month during the academic year (September to April).

\section{Article 10: Amendments}

This constitution shall comprise the operating basis of the PSC.
All amendments to this document must be ratified by a two-thirds vote of the club membership.  
A copy of the amended constitution must be submitted to the Students' Union within two weeks of ratification.   

\end{document}
